### 2017-12-04 manuscript.rmd
moved pneumatophore to own section
added nectosome position reconstruction code with subset of spp and 2 states Dorsal/Ventral

necto_pos = cdata$Nectosome.position
names(necto_pos) = rownames(cdata)

necto_types = cdata$Nectophores
names(necto_types) = rownames(cdata)

@@

```{r simmap_making, echo=F, message=F, warning=F, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
#print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100, message=FALSE) -> necto_types_sim
#print("SIMMAP Bracts")
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
#print("SIMMAP Habitat")
```

@@

@@

>>>>

@@

```{r simmap_making, echo=F, message=F, warning=F, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
#print("SIMMAP Habitat")

#Nectophore position SIMMAP setup
necto_pos_data = cdata[which(cdata$Nectosome.position != "None"),]
necto_pos = necto_pos_data$Nectosome.position
names(necto_pos) = rownames(necto_pos_data)
NectoPosTree = drop.tree(ultratree, which(!(ultratree$tip.label %in% names(necto_pos))))
make.simmap(NectPosTree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
#print("SIMMAP Nectophore Types")
```

@@

###The Gain and Loss of the Pneumatophore

@@

```{r nectosome_pos, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome"}
#SIMMAP NectoPos
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Dorsal", "Ventral")
# necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
# nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(necto_pos_sim)
```
